Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in \textit{Mimulus cardinalis}

### 2016-11-17 ms/ms.Rnw
Added funding info
Deleted files and updated Readme file

%lost on page 11 - extracted and used climate variables
%cartoon of whole procedure for climate variables
% model of growth chamber
% need to explain 'importance'

@@

%* hung up on specialization - clarify? where is ecological oppportunity, tradeoffs, specialization
%	- maybe temporal source-sink makes more sense

@@

@@

% *** Need to fill in exact grant numbers *** %
\section*{Acknowledgements}
Erin Warkman and Lisa Lin helped collect data. CDM was supported by a Biodiversity Postdoctoral Fellowship funded by the NSERC CREATE program. ALA was supported by an NSERC Discovery Grant and a grant from the National Science Foundation.

>>>>

%lost on page 11 - extracted and used climate variables
% need to explain 'importance'

@@

%* hung up on specialization - clarify? where is ecological oppportunity, tradeoffs, specialization

@@

# How similar are focClim and focClimSA?
# summary(mapply(cor, focClim[climVars], focClimSA[climVars]))
# summary(mapply(cor, focClim[climVars], focClimSA[climVars]) ^ 2)

@@

\section*{Acknowledgements}
Erin Warkman and Lisa Lin helped collect data. CDM was supported by a Biodiversity Postdoctoral Fellowship funded by the NSERC CREATE program. ALA was supported by an NSERC Discovery Grant and a grant from the National Science Foundation (DEB 0950171).
